Many-core applications to online track reconstruction in HEP experiments

### 2013-10-03 papers/2013/CHEP/paper.tex
ref and title fixes

\begin{document}
% paper title
\title{Many-core applications to online track reconstruction in HEP experiments}
% Author list
\author{S.~Amerio$^1$, 
  D.~Bastieri$^1$, 
  M.~Corvo$^1$, 
  A.~Gianelle$^1$, 
  W.~Ketchum$^2$,
  T.~Liu$^3$, 
  A.~Lonardo$^4$, 
  D.~Lucchesi$^1$,
  S.~Poprocki$^5$, 
  R.~Rivera$^2$, 
  P.~Vicini$^4$
  and 
  P.~Wittich$^5$,
}
\address{$^1$ INFN and University of Padova, Italy}
\address{$^2$ Los Alamos National Laboratory, New Mexico, USA}
\address{$^3$ Fermi National Accelerator Laboratory, Illinois, USA}
\address{$^4$ INFN Roma, Italy}
\address{$^5$ Cornell University, New York, USA}

>>>>

\begin{document}
% paper title
\title{Many-core applications to online track reconstruction in HEP experiments}
% Author list
\author{S.~Amerio$^1$, 
  D.~Bastieri$^1$, 
  M.~Corvo$^1$, 
  A.~Gianelle$^1$, 
  W.~Ketchum$^2$,
  T.~Liu$^3$, 
  A.~Lonardo$^4$, 
  D.~Lucchesi$^1$,
  S.~Poprocki$^5$, 
  R.~Rivera$^3$, 
  P.~Vicini$^4$
  and 
  P.~Wittich$^5$,
}
\address{$^1$ INFN and University of Padova, Italy}
\address{$^2$ Los Alamos National Laboratory, New Mexico, USA}
\address{$^3$ Fermi National Accelerator Laboratory, Illinois, USA}
\address{$^4$ INFN Roma, Italy}
\address{$^5$ Cornell University, New York, USA}
